Binocular combination in the autonomic nervous system

### 2024-05-22 manuscript.Rmd
Fixed to download individual data files for modelling

if (processdata==2){
# if we're going to need the pre-processed files, extract from zip file
  if (!file.exists(paste0(datadir,'P301_summary.RData'))){
   if (!file.exists(paste0(localdir,'IndividualSummary.zip'))){
          osfnode <- '9ebtd'
          osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)
          fid <- which(osffiles$name=='IndividualSummary.zip')
          osf_download(osffiles[fid,],localdir,progress=TRUE)
   }
          unzip(paste0(localdir,'IndividualSummary.zip'),exdir=datadir)
  }
}

>>>>

if (processdata==2 || domodelling==1){
# if we're going to need the pre-processed files, extract from zip file
  if (!file.exists(paste0(datadir,'P301_summary.RData'))){
   if (!file.exists(paste0(localdir,'IndividualSummary.zip'))){
          osfnode <- '9ebtd'
          osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)
          fid <- which(osffiles$name=='IndividualSummary.zip')
          osf_download(osffiles[fid,],localdir,progress=TRUE)
   }
          unzip(paste0(localdir,'IndividualSummary.zip'),exdir=datadir)
  }
}
